Inference for Trans-dimensional Bayesian Models with Diffusive Nested Sampling

### 2014-07-28 Documents/Paper/ms.tex
Slightly narrower margins
New figure

\documentclass[letterpaper, 11pt]{article}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage[left=3cm,top=3cm,right=3cm]{geometry}
\usepackage{parskip}
\usepackage{amsmath}

@@

>>>>

\documentclass[letterpaper, 11pt]{article}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage[left=2.5cm,top=2.5cm,right=2.5cm]{geometry}
\usepackage{parskip}
\usepackage{amsmath}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{galaxyfield_likelihood.pdf}
\caption{{\bf Top panel: }
The shape of the likelihood function with respect to prior mass for the
GalaxyField data.
{\bf Bottom panel: }The posterior weights of the saved samples. Note the phase
transition at $\log(X) \approx -100$ nats. While this doesn't affect the
posterior distribution (unlike the sinewave example), it would affect calculation
of the marginal likelihood if annealing were used.
\label{fig:sinewaves_likelihood}}
\end{center}
\end{figure}
